Internship Summary: Mid-Term Review

### 2020-07-31 RapportStage/Rapport.tex
coquille remerciement

I would like to sincerely thanks Pierre-François \textsc{LOOS} for supervising my internship. This first experience of academic research in theoretical chemistry confirmed my interest for this domain and taught me many things about theoretical chemistry but also about the job of researcher. I hope that I will have the chance to work in this group agian (and not in the context of a global pandemic if possible). I also thanks my three confined flatmates Tristan, Sylvio and especially Julie for bearing with me during those 3(+2) months.

>>>>

I would like to sincerely thanks Pierre-François \textsc{LOOS} for supervising my internship. This first experience of academic research in theoretical chemistry confirmed my interest for this domain and taught me many things about theoretical chemistry but also about the job of researcher. I hope that I will have the chance to work in this group again (and not in the context of a global pandemic if possible). I also thank my three confined flatmates Tristan, Sylvio and especially Julie for bearing with me during those 3(+2) months.
